Detailed Chemical Abundances with \tc{}

### 2015-09-08 article/ms.tex
Introduce EW

The noise in Equation \ref{eq:cannon} can be taken as a quadrature combination of the pixel uncertainty variance $\sigma_{n\lambda}^2$ and the intrinsic variance of the spectral model at each wavelength $s_\lambda^2$. The flux $f_{n\lambda}$ can be written as a linear function of the label vector, leading to a single-pixel log-likelihood function

@@

Before extending \tc{} to include individual chemical abundances, it is
a useful exercise to understand \textit{why} a simple spectral model can 
approximate synthesis calculations with comparable fidelity. Thus far the applications of \tc{} have been restricted to stellar spectra with resolving powers of $\mathcal{R} = 22,500$ \citep[APOGEE;][]{Ness15a} or less \citep[e.g., LAMOST;][]{Ho15}. In these regimes, the shapes of unsaturated spectral lines are well-represented by Gaussian profiles.

@@

\section*{Acknowledgments}
This research was fostered by discussions at the \textit{New Milky Way}
conference hosted by the Munich Institute for Astro- and Particle Physics, and
the \textit{Stellar Streams in the Local Universe} conference hosted at Ringberg
Castle by the Max-Planck-Institut F\"ur Astronomie. This research made use of 
Astropy, a community-developed core Python package for Astronomy \citep{astropy}.

@@

\section{Appendix A: Reproducing this research}
This \article{} has been compiled from the \texttt{git} repository on \gitAuthorDate{} (commit hash \texttt{\gitAbbrevHash} on \texttt{\gitBranch} branch) hosted online at GitHub\footnote{https://www.github.com/andycasey/fireworks}. The complete data analysis, figures and tables included in this \article{} can be reproduced in full using the following commands in a modern Unix-based terminal:
\vspace{0.5em}

>>>>

The noise (Eq. \ref{eq:cannon}) can be taken as a quadrature combination of the pixel uncertainty variance $\sigma_{n\lambda}^2$ and the intrinsic variance of the spectral model at each wavelength $s_\lambda^2$. The flux $f_{n\lambda}$ can be written as a linear function of the label vector, leading to a single-pixel log-likelihood function

@@

Before extending \tc{} to include individual chemical abundances, it is
a useful exercise to understand \textit{why} a simple spectral model can 
approximate synthesis calculations with comparable fidelity, and thus \textit{how} this framework can be extended to include individual abundances. At present the applications of \tc{} have been restricted to stellar spectra with resolving powers of $\mathcal{R} = 22,500$ \citep[APOGEE;][]{Ness15a} or less \citep[e.g., LAMOST;][]{Ho15}. In these regimes, the shapes of unsaturated spectral lines are well-represented by Gaussian profiles. This fact leads to several critical insights, which we describe below.

In stellar spectroscopy we are frequently presented with the idea of the equivalent width (EW; $\mathcal{W}$) of an absorption line. Consider a single (unblended) atomic line at rest wavelength $\lambda_r$, where the flux values at and surrounding $\lambda_r$ ($f_{n\lambda_r-{\delta}},f_{n\lambda_{r+\delta}}$) are well-approximated by a \textit{Cannon} spectral model. Because the absorption line is well-represented by a Gaussian profile at this spectral resolution, the flux at $\lambda_r$ is related to the EW of the line through

\begin{equation}
\mathcal{W} = \sigma\cdot{}f_{n\lambda_r}\sqrt{2\pi}
\end{equation}

where $\sigma$ is the standard deviation of the profile, which is well-approximated by width of the line spread function (LSF) kernel. That is to say, for resolutions $\mathcal{R} \lesssim 20,000$, $\sigma$ is dominated by the spectrograph, not the absorption line or the labels (stellar parameters).

% where the flux values $f_{n\lambda}$ are well-approximated by the given spectral model.

% Things are Gaussian, therefore EW related.
% How does EW of a line change w.r.t. stellar parameters
% If we had a model for a single line, how could this be included.

@@

\section*{Acknowledgments}
This research was fostered by discussions at the \textit{New Milky Way}
conference hosted by the Munich Institute for Astro- and Particle Physics, and
the \textit{Stellar Streams in the Local Universe} conference hosted at Ringberg
Castle by the Max-Planck-Institut F\"ur Astronomie. This research made use of 
Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
The authors are thankful for the following free online services which help make
science reproducibility easier: GitHub, Travis Continuous Integration, and Zenodo.

@@

\section{Appendix A: Reproducing this research}
This \article{} has been compiled from the \texttt{git} repository (abbreviated commit hash \texttt{\gitAbbrevHash} on \texttt{\gitBranch} branch) hosted online by GitHub at \texttt{github.com/andycasey/fireworks}. The data required to reproduce this analysis is persistently hosted through Zenodo \citep{DATA}. The complete analysis, figures and tables included in this \article{} can be reproduced in full using the following commands in a modern Unix-based terminal:
\vspace{0.5em}
